### 2016-12-05 src/group-2-approximation.tex
foo

\textbf{Remarks:}
We argue that determining if a vertex $v$ can be improved can be done efficiently,
by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
and only ones with positive value.
Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
sum up to more than $val_M(v)$.

\todo[inline]{argue that the number of iteration is bounded}

>>>>

\begin{remark}
Clearly, if the weights on the edges are integral and polynomial bounded the
algorithm runs in polynomial time, this is because in each iteration the
algorithm improves the value of the matching by at least one or otherwise it
terminates.
\end{remark}

\begin{remark}
When the weights are not integral nor polynomial bounded one can use scaling and
rounding first to ensure polynomial runtime in the cost of $\varepsilon$ in the
approximation ratio.
\end{remark}

\begin{remark}
Determining if a vertex $v$ can be improved can be done efficiently
by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
and only ones with positive value.
Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
sum up to more than $val_M(v)$.
\end{remark}
